Shelter System in Toronto Requires Improvement for People's Needs during COVID-19

### 2022-02-05 outputs/paper/paper.Rmd
upadate

By summing up the shelter occupancy counts in every month, we obtain a bar graph Figure \@(fig:bar-plot) to visualize the change of the number of occupancy in each sector. In general, it is clear that the number of shelter occupancy is dropping to almost half of the beginning number from January to December. In January 2020, the shelter occupancy reached its apex, approaching 200,000 people, and for the next two months, the number does not show a declining trend until April. The shelter occupancy was the lowest throughout the whole year at less than 100,000 counts. Besides, the families sector served in all shelters undoubtedly takes the largest proportion of occupancy, meanwhile, youth takes the smallest proportion of occupancy. The men sector has the second most occupancy among all sectors and the co-ed sector's occupancy is similar to the women sector's. This distribution of sector occupancy stays consistent for every single month.

@@

From Figure \@(fig:bar-plot), the youth sector is the smallest portion among all types of sectors. Indeed, there is more aging population looking for shelter beds. Most youth homelessness refers to the young population between 13 and 24 age, and they are independent of their caregivers [@citeho]. The transition from childhood to adulthood is vital that they require social support without a stable source of income. Given one year, around 35,000 to 40,000 youth are experiencing homelessness, and 20% of the homeless in Canada are youth population [@citena]. Homeless youth are distinct from impact adults in that they lack the skills and experiences necessary to make a living. And family conflicts are a primary cause of many youth homeless. Therefore, the youth sector may need extra attention to their emotional, physical and mental development, especially during a pandemic. Due to social distancing and some isolation procedures, they may spend more time staying alone. The shelters with the youth sector should consistently provide programs like skills training, school-based intervention, or family reconnection to make healthy transitions to adulthood.

>>>>

By summing up the shelter occupancy counts in every month, we obtain a bar graph Figure \@ref(fig:bar-plot) to visualize the change of the number of occupancy in each sector. In general, it is clear that the number of shelter occupancy is dropping to almost half of the beginning number from January to December. In January 2020, the shelter occupancy reached its apex, approaching 200,000 people, and for the next two months, the number does not show a declining trend until April. The shelter occupancy was the lowest throughout the whole year at less than 100,000 counts. Besides, the families sector served in all shelters undoubtedly takes the largest proportion of occupancy, meanwhile, youth takes the smallest proportion of occupancy. The men sector has the second most occupancy among all sectors and the co-ed sector's occupancy is similar to the women sector's. This distribution of sector occupancy stays consistent for every single month.

@@

From Figure \@ref(fig:bar-plot), the youth sector is the smallest portion among all types of sectors. Indeed, there is more aging population looking for shelter beds. Most youth homelessness refers to the young population between 13 and 24 age, and they are independent of their caregivers [@citeho]. The transition from childhood to adulthood is vital that they require social support without a stable source of income. Given one year, around 35,000 to 40,000 youth are experiencing homelessness, and 20% of the homeless in Canada are youth population [@citena]. Homeless youth are distinct from impact adults in that they lack the skills and experiences necessary to make a living. And family conflicts are a primary cause of many youth homeless. Therefore, the youth sector may need extra attention to their emotional, physical and mental development, especially during a pandemic. Due to social distancing and some isolation procedures, they may spend more time staying alone. The shelters with the youth sector should consistently provide programs like skills training, school-based intervention, or family reconnection to make healthy transitions to adulthood.
